 Casting multiple shadows: interactive data visualisation with tours and embeddings

### 2020-02-05 paper.Rmd
add in another sentence
refinement, adding in JCGS references

Broadly characterised by @Brehmer2014-hk, characterised two main workflow
steps that an analyst performs when using embedding methods: dimension reduction
and cluster orientation. The first relates to 
dimension reduction achieved by using an embedding method, here an analyst
wants to characterise and map meaning onto the embedded form, for example
identifying batch effects from a high throughput sequencing experiment, or
identifying a gradient along the embedded form. The second relates to using
embeddings as part of a clustering workflow. Here analysts are interested
in identifying  and naming clusters and verifying them by either applying 
known labels or colouring by variables that are a-priori known to distinguish 
clusters.

@@

>>>>

@Brehmer2014-hk characterised two main workflow
steps that an analyst performs when using embedding methods: dimension reduction
and cluster orientation. The first relates to 
dimension reduction achieved by using an embedding method, here an analyst
wants to characterise and map meaning onto the embedded form, for example
identifying batch effects from a high throughput sequencing experiment, or
identifying a gradient along the embedded form. The second relates to using
embeddings as part of a clustering workflow. Here analysts are interested
in identifying  and naming clusters and verifying them by either applying 
known labels or colouring by variables that are a-priori known to distinguish 
clusters. Both of these workflow steps rely on the embedding being 'faithful' to
the underlying high dimensional data, and become much more difficult when
there is no underlying ground truth. A further empirical study by @Sedlmair2013-pn, showed that when using embedding teqhinques, simple 2d scatter plots were an apporiate visualisation to help analysts perform these tasks but they did note that 
depending on the underlying goal multiple dimensionality reduction techniques
are necessary.

@@

- PCA
- tSNE
- UMAP
- PHATE
